Interacting Classical Gas

### 2016-09-05 Interacting Classical Gas_Zhiyu.tex
debug

\subfigure[$E_i=2$]{
\begin{minipage}[b]{0.2\textwidth}
\includegraphics[scale=0.2]{../matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=2_energy.eps}
\includegraphics[scale=0.2]{../matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=2_phasespace.eps}
\end{minipage}
}
\subfigure[$E_i=3$]{
\begin{minipage}[b]{0.2\textwidth}
\includegraphics[scale=0.2]{../matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=3_energy.eps}
\includegraphics[scale=0.2]{../matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=3_phasespace.eps}
\end{minipage}
}
\subfigure[$E_i=5$]{
\begin{minipage}[b]{0.2\textwidth}
\includegraphics[scale=0.2]{../matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=5_energy.eps}
\includegraphics[scale=0.2]{../matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=5_phasespace.eps}
\end{minipage}
}
\subfigure[$E_i=10$]{
\begin{minipage}[b]{0.2\textwidth}
\includegraphics[scale=0.2]{../matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=10_energy.eps}
\includegraphics[scale=0.2]{../matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=10_phasespace.eps}
\end{minipage}
}
\end{center}
\caption{the dependence of beat frequency on internal energy} the upper diagram is the energy of every particle, the lower diagram is the orbit in phase-space, where we see quasi-periodic motion clearly. Here, $E_i$ is large(compare to $F_0\sigma$). In this case, the larger $E_i$ is, the lower the beat frequency is. Actually in very low energy, we can retrieve a beat, but that is for different reason -- it is a beat between $\omega_0$ and $\frac{\omega_0}{2}+\delta $
\label{fig:thermalization1}
\end{figure}

@@

\begin{figure}
\subfigure[]{
\begin{minipage}[b]{0.3\textwidth}
\includegraphics[scale=0.17]{../matlab2016/MolecularDynamics/figure/latexpic/freq_scanE_1.png} 
\end{minipage}
}
\subfigure[]{
\begin{minipage}[b]{0.3\textwidth}
\includegraphics[scale=0.17]{../matlab2016/MolecularDynamics/figure/latexpic/freq_scanE_2.png} 
\end{minipage}
}
\subfigure[]{
\begin{minipage}[b]{0.3\textwidth}
\includegraphics[scale=0.17]{../matlab2016/MolecularDynamics/figure/latexpic/freq_scanE_3.png} 
\end{minipage}
}
\centering
\caption{Frequency of relative motion with internal energy in three regime} Numbers in the legend is the value of $\frac{F_0}{m\omega_0^2\sigma}$
\label{fig:thermalization3}
\end{figure}}
\end{comment}
%-------------%

@@

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.35]{../matlab2016/MolecularDynamics/figure/latexpic/pair1.eps}
\caption{evolution of single-particle energy}
\label{fig:thermalization4}
\end{figure}

@@

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.3]{../matlab2016/MolecularDynamics/figure/latexpic/distribution1_scanF0_E=100_3.eps}
\caption{Distribution $scan F_0, E=100, N=5, \sigma=1$}
\label{fig:thermalization5}
\includegraphics[scale=0.3]{../matlab2016/MolecularDynamics/figure/latexpic/distribution1_scanF0_E=100_3_freq.eps}
\caption{Frequency scan $F_0$, $E=100$, $N=5$, $\sigma=1$}

@@

\begin{figure}
\centering
\includegraphics[scale=0.3]{../matlab2016/MolecularDynamics/figure/latexpic/energyleveljump_fiveparticle_F0=2_1.eps}
\caption{energy of each particle, $F_0=2$}
\label{fig:thermalization6}

\centering
\includegraphics[scale=0.3]{../matlab2016/MolecularDynamics/figure/latexpic/energyleveljump_fiveparticle_F0=10_1.eps}
\caption{energy of each particle, $F_0=10$}
\label{fig:thermalization7}
\end{figure}

@@

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.5]{../matlab2016/MolecularDynamics/figure/latexpic/distribution_at_N=5_F0=10000.eps}
\caption{Energy distribution, N=5, F0=10000}
\label{fig:thermalization8}
\includegraphics[scale=0.47]{../matlab2016/MolecularDynamics/figure/latexpic/distribution_at_N=10_E=1000_edit.eps}
\caption{Energy distribution, N=10, E=1000}
\label{fig:thermalization9}
\includegraphics[scale=0.52]{../matlab2016/MolecularDynamics/figure/latexpic/distribution2_at_N=20_F0=10000.eps} 
\caption{Energy distribution, N=20, F0=10000}
\label{fig:thermalization10}
\end{figure}

@@

\centering
\includegraphics[scale=0.3]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=4E4_N=5.eps}
\caption{N=5,F0=10000,E=1000, initial S=1}
\end{figure}
\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.3]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_4E4_N=5_zoomin1.eps} 
\caption{Zoom in at the beginning part}
\end{figure}
\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.3]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=4E4_N=5_average.eps}
\caption{average over every 30s to see the main tendency}
\label{fig:relaxationPS1}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E3000.eps} 
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E3000_average.eps}
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E3000_sup.eps}
\caption{N=20, F0=1000, E=3000, initial S=1}
Different from N=5 case, this time the fluctuation of S is not that large. In return, with an average over every 30s, the S only fluctuate between 0.5 and 0.2
\label{fig:relaxationPS2}
\end{figure}
\begin{figure}
\centering
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000.eps} 
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_average.eps}
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_sup.eps}
\caption{N=20, F0=1000, E=10000, initial S=1}
\label{fig:relaxationPS3}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0.eps} 
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_average.eps}
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_sup.eps}
\caption{N=20, F0=1000, E=10000, Initial S=0.05}
\label{fig:thermailzationPS4}
\end{figure}

We may zoom in to understand how the distribution cloud is deforming. 
in fig.\ref{fig:relaxationPS5}, we can see some peaks and dips. The peaks are generated by particle ``bumping" (collision process discribed in Breathing frequency, see fig.\ref{Breathingfrequency2}) along the short axis of the cloud, while the dips are generated by ``bumping" along the long axis. Since these bumping only means momentum exchange, after a whole bumping process, the distribution should almost come back. So these peaks and dips will not affect the plateau value, as is shown in fig.\ref{fig:relaxationPS5}
\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_zoom1.eps}
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_zoom2.eps} 
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_zoom3.eps} 
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_zoom4.eps} 
\caption{t=5E3, N=20, F=1000, E=10000, initial S=0, zoom in}
\label{fig:relaxationPS5}
\end{figure}

@@

\centering
\includegraphics[scale=0.8]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=1500_N=50_F10000_E20000_S=1.eps}
\includegraphics[scale=0.8]{../matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=1500_N=50_F10000_E20000_S=1_average.eps} 
\caption{N=50, E=20000, F0=10000 ,t=1500}
\label{fig:relaxationPS6}
\end{figure}

\subsection{Correspondence between energy distribution, behaviour of shape-factor and oscillation of R(t)}
\begin{figure}[hbtp]
\begin{center}
\subfigure[$E=3E5$]{
\begin{minipage}[n]{0.4\textwidth}
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/example_Energy_relaxed_N=20_F0=1E4_E=3E5.eps}
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/example_single-particle-Energy_relaxed_N=20_F0=1E4_E=3E5.eps}
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/example_Shapeav_relaxed_N=20_F0=1E4_E=3E5.eps}   
\end{minipage}
}
\subfigure[$E=2E5$]{
\begin{minipage}[n]{0.4\textwidth}
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/example_Energy_relaxed_N=20_F0=1E4_E=2E5.eps}
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/example_single-particle-Energy_relaxed_N=20_F0=1E4_E=2E5.eps}
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/example_Shapeav_relaxed_N=20_F0=1E4_E=2E5.eps}   
\end{minipage}
}
\subfigure[$E=1E5$]{
\begin{minipage}[n]{0.4\textwidth}
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/example_Energy_relaxed_N=20_F0=1E4_E=1E5.eps}

\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/example_Shapeav_relaxed_N=20_F0=1E4_E=1E5.eps}   
\end{minipage}
}
\subfigure[$E=5E4$]{
\begin{minipage}[n]{0.4\textwidth}

\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/example_Shapeav_relaxed_N=20_F0=1E4_E=5E4.eps}   
\end{minipage}
}
\end{center}
\end{figure}

@@

\newpage
\section{Breathing Frequency}
Usually, to see the response of a quantum gas to a quench, one start from the ground state and suddenly vary some parameter by a little, for instance, $\omega_0'\rightarrow\omega_0=\omega_0'+\Delta\omega$. In that case, one will observe the radius R oscillating at a certain frequency, which is usually called ``breathing mode".
In classical version, the ground state may be meaningless--since classical limit is $\bar{h}\rightarrow 0$, no matter how low the kT is, $kT/\bar{h}$ is always zero so that classical ground state is quite different from the quantum one. Instead, one will expect that the thermalized high temperature classical gas may have something in common with the high excited state of quantum gas. In view of this, if we want to do a quench similar to quantum case, we should begin with a thermalized distribution at $\omega_0'$ and evolve to a new thermalized state at varied $\omega_0$. Furthermore, notice that X and P (normalized) are symmetric for harmonic oscillator. If there is no spontaneous symmetry breaking in phase-space, the distribution cloud should be circular when the gas is completely thermalized. The difference between thermalized cloud before and after quench is  circular under different normalization of phase-space. If we look at both of them in the phase-space normalized according to $\omega_0$, we will find the former one is an ellipse while the latter one is a circle.
If the ellipse is only slightly deviated from circle, the oscillating amplitude will be too small to be distinguished from noise. Therefore, we start from an extreme case -- line distribution (random x, zero p) and observe the oscillation of R(t).
\begin{figure}[hbtp]
\center
\includegraphics[scale=0.8]{../matlab2016/MolecularDynamics/figure/latexpic/freq_scanF_differentE_log.eps}
\caption{breathing mode frequency measured at different E and $F_0$}
\label{Breathingfrequency1}
\end{figure}

@@

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/rotatingframe_example2.eps} 
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/rotatingframe_example1.eps} 
\caption{precession motion in phase-space observed in rotating frame (only show one or two particles' trajectory for clarity)}
\label{Breathingfrequency2}
\end{figure}

@@

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/collision.png}
\caption{a schematic diagram of the collision process}
\label{Breathingfrequency3}
\end{figure}

@@

Let us estimate the precession angle $\alpha$ with $\frac{\sigma}{R}$, which follows from the two-particle analysis. Radius of the cloud R can be estimated according to $E=Nm\omega_0^2R^2$
We will get the precession angular velocity 
\begin{equation}
\delta=2\omega_0\frac{N^\frac{3}{2}m^{\frac{1}{2}}E^{-\frac{1}{2}}\sigma\omega_0}{2\pi}
\label{eq:breathingfrequency1}
\end{equation}
\begin{figure}[hbtp]
\begin{center}
\includegraphics[scale=0.7]{../matlab2016/MolecularDynamics/figure/latexpic/N=5_freq_at_F0=10000_fitting.eps}
\caption{Frequency measured at N=5} 
Since the prediction is only an estimation by order, which means there could be some extra effective coefficient before the R. In view of this, the result is satisfying.

\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/N=5_freq_at_F0=10000_sup1.eps}
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/N=5_freq_at_F0=10000_sup2.eps}
\caption{Spectrum at the beginning and the end of measurement}
\end{center}
 Two spectrum above show the error of our frequency measurement. The line width of the peak is significant compared with the $\delta$. The peak width comes from FT in finite time.
\end{figure}

@@

\centering
\includegraphics[scale=0.7]{../matlab2016/MolecularDynamics/figure/latexpic/N=20_freq_at_F0=10000_2.eps}
\caption{N=20}
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/N=20_freq_at_F0=10000_2_sup1.eps}
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/N=20_freq_at_F0=10000_2_sup2.eps}
\end{figure}

@@

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.4]{../matlab2016/MolecularDynamics/figure/latexpic/N=20_freq_at_differentF0_scanF0_1.eps}
\caption{frequency for N=20}
\end{figure}

>>>>

\subfigure[$E_i=2$]{
\begin{minipage}[b]{0.2\textwidth}
\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=2_energy.eps}
\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=2_phasespace.eps}
\end{minipage}
}
\subfigure[$E_i=3$]{
\begin{minipage}[b]{0.2\textwidth}
\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=3_energy.eps}
\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=3_phasespace.eps}
\end{minipage}
}
\subfigure[$E_i=5$]{
\begin{minipage}[b]{0.2\textwidth}
\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=5_energy.eps}
\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=5_phasespace.eps}
\end{minipage}
}
\subfigure[$E_i=10$]{
\begin{minipage}[b]{0.2\textwidth}
\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=10_energy.eps}
\includegraphics[scale=0.2]{D:/matlab2016/MolecularDynamics/figure/latexpic/twoparticle_Er=10_phasespace.eps}
\end{minipage}
}
\end{center}
\caption{the dependence of beat frequency on internal energy} the upper diagram is the energy of every particle, the lower diagram is the orbit in phase-space, where we see quasi-periodic motion clearly. Here, $E_i$ is large(compare to $F_0\sigma$). In this case, the larger $E_i$ is, the lower the beat frequency is. Actually in very low energy, we can retrieve a beat, but that is for different reason -- it is a beat between $\omega_0$ and $\frac{\omega_0}{2}+\delta $
\label{fig:thermalization1}
\end{figure}

@@

\begin{figure}
\subfigure[]{
\begin{minipage}[b]{0.3\textwidth}
\includegraphics[scale=0.17]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_scanE_1.png} 
\end{minipage}
}
\subfigure[]{
\begin{minipage}[b]{0.3\textwidth}
\includegraphics[scale=0.17]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_scanE_2.png} 
\end{minipage}
}
\subfigure[]{
\begin{minipage}[b]{0.3\textwidth}
\includegraphics[scale=0.17]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_scanE_3.png} 
\end{minipage}
}
\centering
\caption{Frequency of relative motion with internal energy in three regime} Numbers in the legend is the value of $\frac{F_0}{m\omega_0^2\sigma}$
\label{fig:thermalization3}
\end{figure}}
\end{comment}
%-------------%

@@

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.35]{D:/matlab2016/MolecularDynamics/figure/latexpic/pair1.eps}
\caption{evolution of single-particle energy}
\label{fig:thermalization4}
\end{figure}

@@

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution1_scanF0_E=100_3.eps}
\caption{Distribution $scan F_0, E=100, N=5, \sigma=1$}
\label{fig:thermalization5}
\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution1_scanF0_E=100_3_freq.eps}
\caption{Frequency scan $F_0$, $E=100$, $N=5$, $\sigma=1$}

@@

\begin{figure}
\centering
\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/energyleveljump_fiveparticle_F0=2_1.eps}
\caption{energy of each particle, $F_0=2$}
\label{fig:thermalization6}

\centering
\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/energyleveljump_fiveparticle_F0=10_1.eps}
\caption{energy of each particle, $F_0=10$}
\label{fig:thermalization7}
\end{figure}

@@

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution_at_N=5_F0=10000.eps}
\caption{Energy distribution, N=5, F0=10000}
\label{fig:thermalization8}
\includegraphics[scale=0.47]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution_at_N=10_E=1000_edit.eps}
\caption{Energy distribution, N=10, E=1000}
\label{fig:thermalization9}
\includegraphics[scale=0.52]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution2_at_N=20_F0=10000.eps} 
\caption{Energy distribution, N=20, F0=10000}
\label{fig:thermalization10}
\end{figure}

@@

\centering
\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=4E4_N=5.eps}
\caption{N=5,F0=10000,E=1000, initial S=1}
\end{figure}
\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_4E4_N=5_zoomin1.eps} 
\caption{Zoom in at the beginning part}
\end{figure}
\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=4E4_N=5_average.eps}
\caption{average over every 30s to see the main tendency}
\label{fig:relaxationPS1}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E3000.eps} 
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E3000_average.eps}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E3000_sup.eps}
\caption{N=20, F0=1000, E=3000, initial S=1}
Different from N=5 case, this time the fluctuation of S is not that large. In return, with an average over every 30s, the S only fluctuate between 0.5 and 0.2
\label{fig:relaxationPS2}
\end{figure}
\begin{figure}
\centering
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000.eps} 
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_average.eps}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_sup.eps}
\caption{N=20, F0=1000, E=10000, initial S=1}
\label{fig:relaxationPS3}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0.eps} 
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_average.eps}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_sup.eps}
\caption{N=20, F0=1000, E=10000, Initial S=0.05}
\label{fig:thermailzationPS4}
\end{figure}

We may zoom in to understand how the distribution cloud is deforming. 
in fig.\ref{fig:relaxationPS5}, we can see some peaks and dips. The peaks are generated by particle ``bumping" (collision process discribed in Breathing frequency, see fig.\ref{Breathingfrequency2}) along the short axis of the cloud, while the dips are generated by ``bumping" along the long axis. Since these bumping only means momentum exchange, after a whole bumping process, the distribution should almost come back. So these peaks and dips will not affect the plateau value, as is shown in fig.\ref{fig:relaxationPS5}
\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_zoom1.eps}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_zoom2.eps} 
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_zoom3.eps} 
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=5E3_N=20_F1000_E10000_S=0_zoom4.eps} 
\caption{t=5E3, N=20, F=1000, E=10000, initial S=0, zoom in}
\label{fig:relaxationPS5}
\end{figure}

@@

\centering
\includegraphics[scale=0.8]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=1500_N=50_F10000_E20000_S=1.eps}
\includegraphics[scale=0.8]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=1500_N=50_F10000_E20000_S=1_average.eps} 
\caption{N=50, E=20000, F0=10000 ,t=1500}
\label{fig:relaxationPS6}
\end{figure}

\subsection{Correspondence between energy distribution, behaviour of shape-factor and oscillation of R(t)}
\begin{figure}[hbtp]
\begin{center}
\subfigure[$E=3E5$]{
\begin{minipage}[n]{0.4\textwidth}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Energy_relaxed_N=20_F0=1E4_E=3E5.eps}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_single-particle-Energy_relaxed_N=20_F0=1E4_E=3E5.eps}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Shapeav_relaxed_N=20_F0=1E4_E=3E5.eps}   
\end{minipage}
}
\subfigure[$E=2E5$]{
\begin{minipage}[n]{0.4\textwidth}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Energy_relaxed_N=20_F0=1E4_E=2E5.eps}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_single-particle-Energy_relaxed_N=20_F0=1E4_E=2E5.eps}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Shapeav_relaxed_N=20_F0=1E4_E=2E5.eps}   
\end{minipage}
}
\subfigure[$E=1E5$]{
\begin{minipage}[n]{0.4\textwidth}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Energy_relaxed_N=20_F0=1E4_E=1E5.eps}

\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Shapeav_relaxed_N=20_F0=1E4_E=1E5.eps}   
\end{minipage}
}
\subfigure[$E=5E4$]{
\begin{minipage}[n]{0.4\textwidth}

\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Shapeav_relaxed_N=20_F0=1E4_E=5E4.eps}   
\end{minipage}
}
\end{center}
\end{figure}

@@

\newpage
\section{Breathing Frequency}
Usually, to see the response of a quantum gas to a quench, one start from the ground state and suddenly vary some parameter by a little, for instance, $\omega_0'\rightarrow\omega_0=\omega_0'+\Delta\omega$. In that case, one will observe the radius R oscillating at a certain frequency, which is usually called ``breathing mode".
In classical version, the ground state may be meaningless--since classical limit is $\bar{h}\rightarrow 0$, no matter how low the kT is, $kT/\bar{h}$ is always zero so that classical ground state is quite different from the quantum one. Instead, one will expect that the thermalized high temperature classical gas may have something in common with the high excited state of quantum gas. In view of this, if we want to do a quench similar to quantum case, we should begin with a thermalized distribution at $\omega_0'$ and evolve to a new thermalized state at varied $\omega_0$. Furthermore, notice that X and P (normalized) are symmetric for harmonic oscillator. If there is no spontaneous symmetry breaking in phase-space, the distribution cloud should be circular when the gas is completely thermalized. The difference between thermalized cloud before and after quench is  circular under different normalization of phase-space. If we look at both of them in the phase-space normalized according to $\omega_0$, we will find the former one is an ellipse while the latter one is a circle.
If the ellipse is only slightly deviated from circle, the oscillating amplitude will be too small to be distinguished from noise. Therefore, we start from an extreme case -- line distribution (random x, zero p) and observe the oscillation of R(t).
\begin{figure}[hbtp]
\center
\includegraphics[scale=0.8]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_scanF_differentE_log.eps}
\caption{breathing mode frequency measured at different E and $F_0$}
\label{Breathingfrequency1}
\end{figure}

@@

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotatingframe_example2.eps} 
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/rotatingframe_example1.eps} 
\caption{precession motion in phase-space observed in rotating frame (only show one or two particles' trajectory for clarity)}
\label{Breathingfrequency2}
\end{figure}

@@

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/collision.png}
\caption{a schematic diagram of the collision process}
\label{Breathingfrequency3}
\end{figure}

@@

Let us estimate the precession angle $\alpha$ with $\frac{\sigma}{R}$, which follows from the two-particle analysis. Radius of the cloud R can be estimated according to $E=Nm\omega_0^2R^2$
We will get the precession angular velocity 
\begin{equation}
\delta=2\omega_0\frac{N^\frac{3}{2}m^{\frac{1}{2}}E^{-\frac{1}{2}}\sigma\omega_0}{2\pi}
\label{eq:breathingfrequency1}
\end{equation}
\begin{figure}[hbtp]
\begin{center}
\includegraphics[scale=0.7]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=5_freq_at_F0=10000_fitting.eps}
\caption{Frequency measured at N=5} 
Since the prediction is only an estimation by order, which means there could be some extra effective coefficient before the R. In view of this, the result is satisfying.

\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=5_freq_at_F0=10000_sup1.eps}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=5_freq_at_F0=10000_sup2.eps}
\caption{Spectrum at the beginning and the end of measurement}
\end{center}
 Two spectrum above show the error of our frequency measurement. The line width of the peak is significant compared with the $\delta$. The peak width comes from FT in finite time.
\end{figure}

@@

\centering
\includegraphics[scale=0.7]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=20_freq_at_F0=10000_2.eps}
\caption{N=20}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=20_freq_at_F0=10000_2_sup1.eps}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=20_freq_at_F0=10000_2_sup2.eps}
\end{figure}

@@

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=20_freq_at_differentF0_scanF0_1.eps}
\caption{frequency for N=20}
\end{figure}
